High Resolution Identification of Protein-DNA Binding Events and Quality Control for ChIP-exo data

### 2015-11-21 rmarkdown/chip_exo_paper.Rnw
Changed asses to assess in paper

    In this article we provide a quality control pipeline which
    visually asses ChIP-exo biases and calculates a signal-to-noise
    measure. Also, we updated dPeak \cite{dpeak}, which makes a
    striking balance in sensitivity, specificity and spatial
    resolution for ChIP-exo data analysis.

@@

Figure \ref{fig:qcdiagram} shows a flowchart for the ChIPexoQC
pipeline. Which basically partitions the genome by keeping the
non-digested ChIP-exo regions. Then, for each region it calculates a
series of statistics. Finally, it creates several visualizations
designed to asses the quality levels of a ChIP-exo sample.

@@

In order to asses the strand imbalance we created the following
visualization presented in figure \ref{fig:strand}. A) shows the FSR's
behavior as lower depth regions are being filtered out, while B) shows
which percentage of the regions are composed by fragments of both
strands or only one (forward or backward). As the number of reads per
region's lower bound increases, the quantiles tend to approach the
median. To evaluate this statement, for each replicate of the FoxA1
dataset, we divided the regions formed by at least \Sexpr{de}
fragments into into the ones that overlap with any of the sample's
peaks. The p.value for ERR36935 is \Sexpr{pval[[1]]}, for ERR336942 is
\Sexpr{pval[[2]]} and for ERR336956 is \Sexpr{pval[[3]]}. This shows
that only the middle sample from figure \ref{fig:strand} is the least
imbalance sample from the the three, while the other two still show a
higher imbalance at the \Sexpr{de} level.

@@

We provide a ChIP-exo QC pipeline capable of asses the balance between
enriched samples and low complexity regions. It is shown that the
``peak-pair'' assumption doesn't hold in practice and we provide two
out-of-the-box visualization capable to asses the strand imbalance in
a ChIP-exo experiment.

>>>>

    In this article we provide a quality control pipeline which
    visually assess ChIP-exo biases and calculates a signal-to-noise
    measure. Also, we updated dPeak \cite{dpeak}, which makes a
    striking balance in sensitivity, specificity and spatial
    resolution for ChIP-exo data analysis.

@@

Figure \ref{fig:qcdiagram} shows a flowchart for the ChIPexoQC
pipeline. Which basically partitions the genome by keeping the
non-digested ChIP-exo regions. Then, for each region it calculates a
series of statistics. Finally, it creates several visualizations
designed to assess the quality levels of a ChIP-exo sample.

@@

In order to assess the strand imbalance we created the following
visualization presented in figure \ref{fig:strand}. A) shows the FSR's
behavior as lower depth regions are being filtered out, while B) shows
which percentage of the regions are composed by fragments of both
strands or only one (forward or backward). As the number of reads per
region's lower bound increases, the quantiles tend to approach the
median. To evaluate this statement, for each replicate of the FoxA1
dataset, we divided the regions formed by at least \Sexpr{de}
fragments into into the ones that overlap with any of the sample's
peaks. The p.value for ERR36935 is \Sexpr{pval[[1]]}, for ERR336942 is
\Sexpr{pval[[2]]} and for ERR336956 is \Sexpr{pval[[3]]}. This shows
that only the middle sample from figure \ref{fig:strand} is the least
imbalance sample from the the three, while the other two still show a
higher imbalance at the \Sexpr{de} level.

@@

We provide a ChIP-exo QC pipeline capable of assess the balance between
enriched samples and low complexity regions. It is shown that the
``peak-pair'' assumption doesn't hold in practice and we provide two
out-of-the-box visualization capable to assess the strand imbalance in
a ChIP-exo experiment.
